---
title: 'Career path in Research Software Community in United-Kingdom'
author: "Olivier PHILIPPE"
date: "26 June 2016"
output:
    html_document:
        keep_md: yes
        number_sections: yes
        toc_depth: 4
    github_document:
        md_extensions: -autolink_bare_uris+hard_line_breaks
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
    # Setting up the directory
    ## Work only on linux -- if it is not working needs to insert manually
    this.dir = system("pwd", intern = T) 
    setwd(this.dir)
    setwd('~/git/ssi/RSE-Survey-2016/')
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
    knitr::read_chunk('/home/olivier/git/ssi/RSE-Survey-2016/R/career_path.R')
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
    knitr::read_chunk('/home/olivier/git/ssi/RSE-Survey-2016/R/uni_test.R')
```

```{r loadFile, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r sourceFunc, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r loadLibrary, echo=FALSE, message=FALSE, warning=FALSE}
```

```{r testUni}
```

# Introduction

One problematic inherent to any emergence of a new role within well establish structure (here the university), it is the difficulty to have a clear career path for the people that are coming to fill that new role. 
This problem directly hits the community of Research Software Engineers in United-Kingdom.
One indicator that can be used to assess this problematic is the salary range. 

```{r salaryUnivariate}
```

These results alone do not necessarily give a good picture to the problem. One thing to do is to compare these results with the data about the academic staff in UK. 
We collected the data from [HESA](https://www.hesa.ac.uk/intros/staffintro1415) (accessed on the 02/07/16) to get the information about the repartition of salary in academy in UK. 
The range used in their survey is slighty different than the one we used for our survey. We created a new range of salary that establish a correspondance between their ranges and ours. However, the categories can sometime overlap. Therefore, the 


```{r testCareer}
```