---
title: "RSE Survey 2016"
author: "Olivier PHILIPPE"
date: "26 June 2016"
output:
  html_document:
    keep_md: yes
    number_sections: yes
    toc_depth: 4
  github_document:
    md_extensions: -autolink_bare_uris+hard_line_breaks
  pdf_document:
    toc_depth: '4'
---

```{r package_options, include=FALSE}
    # Specfy the output format
    options(knitr.table.format = 'markdown')
    # Specify global option for the figures
    knitr::opts_chunk$set(fig.width = 20, fig.height = 15)
    knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, dev=c('png'))
```

```{r}
    # Setting up the directory
    ## Work only on linux -- if it is not working needs to insert manually
    this.dir = system("pwd", intern = T) 
    setwd(this.dir)
    setwd('~/git/ssi/RSE-Survey-2016/')
```

```{r}
    knitr::read_chunk('/home/olivier/git/ssi/RSE-Survey-2016/R/univariate_analysis.R')
```

```{r sourceFunc}
```

```{r loadLibs}
```

```{r loadFile}
```

```{r disciplinePrep}
```

```{r disciplineTable}
```

```{r disciplinePlot, fig.width=20, fig.height=20}
```

```{r educationPrep}
```


```{r educationTable}
```

```{r educationPlot}
```

```{r genderPrep}
```

```{r genderTable}
```

```{r genderPlot}
```

```{r genderAllPrep}
```

```{r genderAllPlot, fig.width=20, fig.height=20}
```

```{r contractPrep}
```

```{r contractTable}
```

```{r contractPlot}
```


```{r salaryPrep}
```

```{r salarayTable}
```

```{r salaryPlot}
```

```{r salaryAllPrep}
```

```{r salaryAllPlot}
```

```{r busFactorPrep}
```

```{r busFactorTable}
```

```{r busFactorPlot}
```

```{r handOverPrep}
```

```{r handOverTable}
```

```{r handOverPlot}
```

```{r contribYNPrep}
```

```{r contribYNTable}
```

```{r contribYNPlot}
```

```{r contribAllPrep}
```

```{r contribAllPlot}
```

```{r workIndicatorPrep}
```

```{r workIndicatorPlot}
```

```{r careerPrep}
```

```{r careerPlot}
```

# Wordclouds

We asked three separated questions to capture the variety of skills and tools that are important for an RSE. Each questions offered the opportunity to fills three freetext fields. These questions help us to get a gist of what is important for RSE on a more braod and less defined way. 
The following wordclouds give an idea of that aspect, without pretenting to be rigourous. 


## Most important skills for an RSE

```{r skillImportantPrep}
```

```{r skillImportantPlot, fig.width=5, fig.height=5}
```

## Most important skills to improve for an RSE

```{r skillImprovePrep}
```

```{r skillImprovePlot, fig.width=5, fig.height=5}
```

## Most important tool for an RSE

```{r toolPrep}
```

```{r toolPlot, fig.width=5, fig.height=5}
```
