---
title: "RSE Survey 2016"
author: "Olivier PHILIPPE"
date: "26 June 2016"
output:
  html_document:
    keep_md: yes
    number_sections: yes
    toc_depth: 4
  github_document:
    md_extensions: -autolink_bare_uris+hard_line_breaks
  pdf_document:
    toc_depth: '4'
---

```{r package_options, include=FALSE}
    # Specfy the output format
    options(knitr.table.format = 'markdown')
    # Specify global option for the figures
    knitr::opts_chunk$set(fig.width = 20, fig.height = 15)
    knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, dev=c('png'))
```

```{r}
    # Setting up the directory
    ## Work only on linux -- if it is not working needs to insert manually
    this.dir = system("pwd", intern = T) 
    setwd(this.dir)
    setwd('~/git/ssi/RSE-Survey-2016/')
```

```{r}
    knitr::read_chunk('/home/olivier/git/ssi/RSE-Survey-2016/R/univariate_analysis.R')
```

```{r sourceFunc}
```

```{r loadLibs}
```

```{r loadFile}
```

```{r disciplinePrep}
```

```{r disciplineTable}
```

```{r disciplinePlot, fig.width=20, fig.height=20}
```

```{r educationPrep}
```


```{r educationTable}
```

```{r educationPlot}
```

```{r genderPrep}
```

```{r genderTable}
```

```{r genderPlot}
```

```{r genderAllPrep}
```

```{r genderAllPlot, fig.width=20, fig.height=20}
```

```{r contractPrep}
```

```{r contractTable}
```

```{r contractPlot}
```

```{r firstJobPrep}
```

```{r firstJobTable}
```

```{r firstJobPlot}

```{r salaryPrep}
```

```{r salarayTable}
```

```{r salaryPlot}
```

```{r salaryAllPrep}
```

```{r salaryAllPlot}
```

```{r busFactorPrep}
```

```{r busFactorTable}
```

```{r busFactorPlot}
```

```{r handOverPrep}
```

```{r handOverTable}
```

```{r handOverPlot}
```

```{r contribYNPrep}
```

```{r contribYNTable}
```

```{r contribYNPlot}
```

```{r contribAllPrep}
```

```{r contribAllPlot}
```

# Work Indicators

## Introduction
How to measure the quality of a job has been debated in psychology for a long time [4]. Several models exist to understand the link between different factors of job satisfaction and turnover intention [5]–[9].
 Turnover intention is an important measure that is highly associated with the risk of employees leaving the organisation [7].
Job satisfaction is important in retaining RSEs. Perceived employability provides information on how workers values their own skills in regard of the market.
To measure the different attitudes toward the RSE role, we used scales that have been created in [5], [6], [8], [9].
These are Likert scale [10], which are 5 point ordinal scales graduated from Strongly disagree to Strongly agree.
Each scale is composed of several so called items (i.e. questions) that each measure one attitude.

### Turnover intention

```{r TurnOverPrepare}
```

```{r TurnOverQ}
```

```{r TurnOverStackTime, fig.width = 20, fig.height = 5}
```

```{r TurnOverStackAgree, fig.width = 20, fig.height = 3}
```

### Perceived Employability

```{r PerceivedEmpPrepare}
```

```{r PerceivedEmpQ}
```

```{r PerceivedEmpStack, fig.width = 20, fig.height = 5}
```

### Satisfaction

```{r SatisfactionPrepare}
```

```{r SatisfactionQ}
```

```{r  StatisfactionStack, fig.width = 20, fig.height = 5}
```


### Recognition

```{r RecognitionPrepare}
```

```{r RecognitionQ}
```

```{r RecognitionStack, fig.width = 20, fig.height = 5}
```


### Feedback

```{r FeedbackPrepare}
```

```{r FeedbackQ}
```

```{r FeedbackStack, fig.width = 20, fig.height = 8}
```

## Summary

```{r workIndicatorPrep}
```

```{r workIndicatorPlot}
```

# Career Plan

## Introduction

```{r careerStackPrep}
```

```{r careerStackPlot, fig.width=20, fig.height=5}
```

```{r careerPrep}
```

```{r careerPlot}
```

# Wordclouds

We asked three separated questions to capture the variety of skills and tools that are important for an RSE. Each questions offered the opportunity to fills three freetext fields. These questions help us to get a gist of what is important for RSE on a more braod and less defined way. 
The following wordclouds give an idea of that aspect, without pretenting to be rigourous. 


## Most important skills for an RSE

```{r skillImportantPrep}
```

```{r skillImportantPlot, fig.width=5, fig.height=5}
```

## Most important skills to improve for an RSE

```{r skillImprovePrep}
```

```{r skillImprovePlot, fig.width=5, fig.height=5}
```

## Most important tool for an RSE

```{r toolPrep}
```

```{r toolPlot, fig.width=5, fig.height=5}
```
